R Notebook for MSDepression Project

### 2022-08-05 lab_notebook/lab_notebook.Rmd
Add files via upload

>>>>

#### 20220805
[x] trying out correlations with effect sizes instead of Ts, wow this makes results even better, they all work

#### 20220810
[x] make sure the mutate command is okay, somehow I think we might be undercounting the healthy group. Okay ish now, but somehow the depGroupVar has a lower number than chaining together this command:  df_good_mimosa_unique %>% filter(Has.depdx == FALSE) %>% filter(On.Antidepressants == FALSE) %>% filter(PHQ.2_zero == TRUE). Double checked the logic and it looks okay
- I think it has something to do with when I include people if they have a positive PHQ2 OR 9 (PHQ2 | PHQ9): Checked this, the | works just fine
- Will need to make sure to write the draw io to match my mutate commands. Must be that when I do the filter separately, I am counting some 0s that I shouldn't be counting in phq2.
